|

### 2023-12-06 manuscript/manuscript_2.0.Rmd
further advances in hte revision

In dominance and aggressive interactions, a crucial piece of
information to guide individual actions is the fighting ability of interacting 
partners, which is sometimes referred to as Resource Holding Potential 
[RHP, Parker -@parker_Assessment_1974] or simply as quality. 
Responsiveness to the quality of an opponent is central 
to communication systems in which individuals 
exhibit badges of status, where a signal typically conveys quality 
[@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Such signals tend to be arbitrary, however, meaning the signals could potentially be 
produced by high- and low-quality individuals alike, opening up the 
possibility of dishonest signalling and raising the question of evolutionary stability. 
Signals can be evolutionarily stable whenever low-quality individuals 
pay a higher fitness cost for carrying the signal such that it is not 
in the interest of low-quality individuals to fake quality by producing a large badge.
Signal costs inversely proportional to quality may come about as a result of the
production costs of the signal, in which case the signal works like a handicap
[@botero_Evolution_2010; @johnstone_Badges_1993;@grafen_Biological_1990;@zahavi_Mate_1975]. 
Alternatively, the costs can come from 
the aggressive reaction of receivers when the convention of the communication 
is broken [@enquist_Signaling_2010;@tibbetts_Socially_2004]. For example in paper 
wasps, subordinate individuals with experimentally manipulated dominant-like facial
patterns received more aggression from the dominant [@tibbetts_Socially_2004]. 
In this case, costs are socially rather than developmentally mediated and are 
triggered by the violation of the convention, although how the convention
is established in the first place is unclear.

>>>>

In dominance and aggressive interactions, a crucial piece of
information to guide individual actions is the fighting ability of interacting 
partners, which is sometimes referred to as Resource Holding Potential 
[RHP, Parker -@parker_Assessment_1974] or simply as quality. 
Responsiveness to the quality of an opponent is central 
to communication systems in which individuals 
exhibit badges of status, where a signal typically conveys quality 
[@johnstone_Badges_1993; @rohwer_Social_1975a]. 
Such signals tend to be arbitrary, however, meaning the signals could potentially be 
produced by high- and low-quality individuals alike, opening up the 
possibility of dishonest signalling and raising the question of evolutionary stability. 
Signals can be evolutionarily stable whenever low-quality individuals 
pay a higher fitness cost for carrying the signal such that it is not 
in the interest of low-quality individuals to fake quality by producing a large badge.
Signal costs inversely proportional to quality may come about as a result of the
production costs of the signal, in which case the signal works like a 'handicap'
[@botero_Evolution_2010; @johnstone_Badges_1993;@grafen_Biological_1990;@zahavi_Mate_1975].
Throughout this manuscript, we use the word 'handicap' to refer to the differential 
costs model by Grafen [-@grafen_Biological_1990]
Alternatively, the costs can come from 
the aggressive reaction of receivers when the convention of the communication 
is broken [@enquist_Signaling_2010;@tibbetts_Socially_2004]. For example in paper 
wasps, subordinate individuals with experimentally manipulated dominant-like facial
patterns received more aggression from the dominant [@tibbetts_Socially_2004]. 
In this case, costs are socially rather than developmentally mediated and are 
triggered by the violation of the convention, although how the convention
is established in the first place is unclear.
